---
title: "Setting up your computer for the LimeSurvey API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setting up your computer for the LimeSurvey API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

In order to use the LimeSurvey API, you first have to setup your computer with 
the neccesary credentials.

These credentials are the name of your company account in your LimeSurvey 
website, your user name and your password.

As we use R to communicate with the API, we will put these credentials in 
environment variables which are stored in the file .Renviron where our R code will find it.

You can open this file on your machine by first installing the `{usethis}` package and then using the `edit_r_environ()` function:

```{r, eval=FALSE}
usethis::edit_r_environ();
```

Then, add these 3 lines to this file (always finish with a new line!) and save:

```
LIMESURVEY_HOST="PUT THE DOMAIN NAME OF YOUR LIMESURVEY INSTALLATION HERE!"
LIMESURVEY_USER="PUT YOUR USER NAME HERE!"
LIMESURVEY_PW="PUT YOUR PASSWORD HERE!"
```

To load these environment variables into your R session, you have to 
enter the following commands into your R console.

```{r, eval=FALSE}

### Load the LimeSurvey environment variables into your R session:

options(
  lime_api =
    paste0(
      "https://", Sys.getenv("LIMESURVEY_HOST"), "/admin/remotecontrol"
    )
  );
options(lime_username = Sys.getenv("LIMESURVEY_USER"));
options(lime_password = Sys.getenv("LIMESURVEY_PW"));

```

You can store these commands in your `.Rprofile` file, in order to have them 
persistently available in every R session.

You can open your `.Rprofile` file with the command

```{r, eval=FALSE}
usethis::edit_r_profile();
```

Finally you just have to restart R (enter `ctrl` + `shift` + `F10` in RStudio).

And voilà! Now, you should be able to communicate with the LimeSurvey API with the  function `limer_upload_tsv_to_limesurvey()` or other functions of this package.

